### 2013-11-21 loadClean.Rmd
Changed the toc font size in css

names(perGini2006) <- c("cntry","perGini")
macro2006 <- merge(q309_06w,poverty_06w,by="cntry",all.x=TRUE)
macro2006 <- merge(macro2006,perGini2006,by="cntry",all.x=TRUE)
macro2006$year <- 2006

#macro <- rbind(macro2006,macro2010)
### ------ END 2006 ---------- ####
```

>>>>

names(perGini2006) <- c("cntry","perGini")
macro2006 <- merge(q309_06w,poverty_06w,by="cntry",all.x=TRUE)
macro2006 <- merge(macro2006,perGini2006,by="cntry",all.x=TRUE)
macro2006$year <- 2006
```
